Realizing Temporal Graphs

### 2022-11-30 RealizingTemporalGraphs.tex
Wednesday 30th November

>>>>

\section{FPT and W[1]-hardness of exact realization}
In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.

\begin{theorem}
    \deltaExactLong\ is FPT parameterized by the feedback edge number.
\end{theorem}

Let $D$ be an instance of \deltaExact, with $G$ being its underlying graph.
We solve the problem using the following steps.
\begin{enumerate}
    \item Create $G'$ and $D'$ from $G$ and $D$ respectively, by removing all degree $1$ vertices from $G$ and $D$.
    \item Compute a minimum feedback edge set $F$ in $G'$.
    \item Determine $O(k)$ vertices of interest $U$ of $G'$, where $k = |F|$.
    \item Find the (partial) labelling of $G'$, that connects all pairs of vertices from $U$, satisfying their respective values in $D'$.
    \item Fill in the labeling for whole $G'$.
    \item Fill in the labeling for $G$, respecting $D$.
\end{enumerate}
